Classless Java: Tuning Java Interfaces

### 2015-12-07 paper/sections/Implementation.tex
revised S6

>>>>

\paragraph{Lombok does Language tuning}
We consider Lombok to be the most developed example of language
tuning.  While the authors of Lombok do not introduce a specific term
for what they are doing, their slogan \emph{``Spice up your java''}
seems to be in line with the philosophy of language tuning. Some
other examples of language tuning in Lombok include the \Q@val@ type,
similar to \Q@auto@ in C\# or C++04.  Another library doing language
tuning is CoFoJa~\cite{}\bruno{reference}, where annotations are used to insert
pre-post conditions in generated bytecode.
